\begin{abstract}
Matrix factorization (MF) has been one of most popular method in collaborative filtering, one of the main approach in recommendation system. However, facing the challenges of cold start and sparsity, many researchers have tried to incorporate side information such text information of item, social network to improve the recommendation accuracy. Among all kinds of information, social connection stands out because it conforms to the reality that people are affected by each other in the social network, which is contrary to the assumption in standard MF that users are independent and identically distributed (i.i.d). Therefore, there are many research work in the literature integrating social information as regularization terms into the MF framework, which constrains a user's latent vector closer to those have relations with him/her. The relations can be following  or trust in social network. However, most of the previous work require that explicit relations exist between users while those relations are not always accessible. Besides, it's very intuitive that we may trust our friends concerning different domains rather than all domains. Taking the two things into account, an Implicit Domain-Specific Recommendation (IDSR) model is proposed in this paper, which tries to infer the implicit trust and domain to improve the MF framework. Experimental result in real dataset shows the improving recommendation accuracy comparing to several baseline method, which demonstrate the effectiveness of the method.
\end{abstract}